Flowchart of Current Algorithm

### 2009-04-23 docs/flowchart/flowchart.tex
made notation consisten with new w0 spherical stuff

We begin with equation (23) in paper III written in spherical coordinates:
\[
\frac{1}{r^2}\frac{\partial}{\partial r} \left (r^2 \beta_0 w_0 \right ) =
\beta_0 \left ( \Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} \right )\enskip.
\]
We expand the spatial derivative and divide through by $\beta_0$:
\begin{equation}
\label{eq:sphconstraint}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0 \right ) +
w_0 \frac{1}{\beta_0} \frac{\partial \beta_0}{\partial r} =
 \Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t}  \enskip .
\end{equation}
Recalling from paper I that;
\[
\frac{1}{\gammabar p_0}  \frac{\partial p_0}{\partial r} = \frac{1}{\beta_0} \frac{\partial \beta_0}{\partial r}\enskip,
\]
and moving this term to the right hand side,
we can express equation (\ref{eq:sphconstraint}) as:
\begin{eqnarray}
%\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0 \right ) +
%w_0 \frac{1}{\gammabar p_0}  \frac{\partial p_0}{\partial r} &=&
% \left ( \Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} \right ) \nonumber \\
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0 \right ) &=&
  \Sbar - \frac{1}{\gammabar p_0} \left( 
\frac{\partial p_0}{\partial t} + w_0 \frac{\partial p_0}{\partial r} \right)\enskip. \label{eq:w01}
\end{eqnarray}
We first solve a piece of this equation for $\ow = w_0 - \dw$:
\begin{eqnarray}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 \ow \right ) &=& \Sbar \enskip.
\end{eqnarray}
Then we can write
\begin{eqnarray}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 \dw \right ) &=&
  - \frac{1}{\gammabar p_0} \left(
\frac{\partial p_0}{\partial t} + (\ow + \dw)
\frac{\partial p_0}{\partial r} \right)\enskip.\label{eq:w01a}
\end{eqnarray}

Multiplying equation (\ref{eq:w01a}) through by $\gammabar p_0 $,
taking another derivative with respect to $r$, and switching the order
of temporal and spatial derivatives, we get:
\begin{equation}
\label{eq:sphconstraint_2}
\frac{\partial}{\partial r} \left [ \frac{\gammabar p_0 }{r^2} \frac{\partial}{\partial r} (r^2 \dw) \right ]
= -\frac{\partial}{\partial t} \frac{\partial p_0}{\partial r}
  -\frac{\partial}{\partial r} \left ((\ow+\dw) \frac{\partial p_0}{\partial r} \right )\enskip.
\end{equation}

To solve for $\dw$ we will need to substitute for the derivatives of $p_0.$
To do so we start with the equation of hydrostatic equilibrium in a spherical geometry:
\[
\frac{\partial p_0}{\partial r} = -\rho_0 g \, ; \quad
g = \frac{G m_\mathrm{encl}}{r^2}\enskip,
\]
where $m_\mathrm{encl}(r)$ is the mass enclosed at radius $r$ and $G$ is the
gravitational constant.  
Using this, we can then write equation (\ref{eq:sphconstraint_2}) as:
\begin{eqnarray}
\frac{\partial}{\partial r} \left[ \frac{\gammabar p_0}{r^2} \frac{\partial}{\partial r} (r^2 \dw) \right] &=&
 \frac{\partial}{\partial t} \left (\rho_0 g \right )
+\frac{\partial}{\partial r} \left (w_0 \rho_0 g \right) \nonumber \\
&=&
  g \left[ \frac{\partial \rho_0}{\partial t} + \frac{\partial}{\partial r} (w_0 \rho_0) \right]
+ \rho_0 \left( \frac{\partial g}{\partial t} + w_0 \frac{\partial g}{\partial r} \right) \enskip.\nonumber\\
&&
\label{eq:sphconstraint_3}
\end{eqnarray}
The mass enclosed inside any radius, $r$, is $m_\mathrm{encl}(r) = 4 \pi
\int_0^r \rhozero(s) s^2 ds$, or alternately, $\partial m_\mathrm{encl}/\partial r = 4\pi r^2 \rho_0$.  
The Lagrangian derivative of the enclosed mass is then:
\begin{eqnarray}
\frac{D_0 m_\mathrm{encl}}{D t} &=& \frac{\partial m_\mathrm{encl}}{\partial t} + w_0 \frac{\partial m_\mathrm{encl}}{\partial r} \nonumber \\
 &=& 4\pi \left( \frac{\partial}{\partial t} \int_0^r \rhozero(s) s^2 ds + w_0 r^2 \rho_0 \right) \nonumber \\
&=& 4\pi \left( \int_0^r \frac{\partial \rho_0}{\partial t} s^2 ds + w_0 r^2 \rho_0 \right) \nonumber \\
&=& 4\pi \left\{ -\int_0^r \left [ \frac{1}{s^2}\frac{\partial(s^2 \rho_0 w_0)}{\partial s} + \frac{1}{s^2}\frac{\partial (s^2 \etarho)}{\partial s} \right ]s^2 ds + w_0 r^2 \rho_0 \right\} \nonumber \\
&=&  \left . 4\pi \left(-s^2 \rho_0 w_0 \right |_0^r - \left . s^2 \etarho \right |_0^r + w_0 r^2 \rho_0 \right) \nonumber \\
&=& -4\pi r^2 \etarho \label{eq:dmdt}
\end{eqnarray}
where we used the spherical form of equation (29) in paper III, 
\begin{equation}
\label{eq:sph_continuity}
\frac{\partial \rhozero}{\partial t} + \frac{1}{r^2} \frac{\partial (r^2 \rho_0 w_0)}{\partial r} 
+ \frac{1}{r^2} \frac{\partial (r^2 \etarho )}{\partial r}  = 0 \enskip ,
\end{equation}
to eliminate $\partial \rho_0/\partial t$.  We note that in the
absence of any mixing, $\etarho=0$, and  $D_0 m_\mathrm{encl}/Dt = 0.$
%which is another way of saying that the mass inside a fluid element
%does not change during expansion.  
Equation (\ref{eq:dmdt})
allows us to write the Lagrangian change in the gravitational
acceleration as:
\begin{eqnarray}
\frac{D_0 g}{D t} = \frac{\partial g}{\partial t} + w_0 \frac{\partial g}{\partial r} &=& \frac{D_0}{Dt}\left(\frac{G m_\mathrm{encl}}{r^2}\right) \nonumber \\
&=& G m_\mathrm{encl}\frac{D_0}{D t}\left(\frac{1}{r^2}\right) + \frac{G}{r^2}\frac{D_0 m_\mathrm{encl}}{Dt} \nonumber \\
&=& -\frac{2 w_0 G m_\mathrm{encl}}{r^3} - 4 \pi G \etarho \nonumber \\
&=& -\frac{2 w_0 g}{r} - 4 \pi G \etarho \enskip .
\end{eqnarray}

Putting it all together, equation (\ref{eq:sphconstraint_3}) becomes:
\begin{equation}
 \frac{\partial}{\partial r} \left[ \frac{\gammabar p_0}{r^2} \frac{\partial}{\partial r} (r^2 \dw) \right] 
= 
  g \left [ \frac{\partial \rho_0}{\partial t} + \frac{\partial}{\partial r} (w_0 \rho_0) \right ]
+ \rho_0 \left(\frac{-2 w_0 g}{r} - 4 \pi G \etarho \right) \label{eq:B5} \enskip.
\end{equation}
Finally, we can use equation (\ref{eq:sph_continuity})
to write equation (\ref{eq:B5}) as:
\begin{eqnarray}
\frac{\partial}{\partial r} \left[ \frac{\gammabar p_0}{r^2} \frac{\partial}{\partial r} (r^2 \dw) \right] && \nonumber \\
&=&
 g \left [ -\frac{1}{r^2} \frac{\partial}{\partial r} (r^2 w_0 \rhozero)
           -\frac{1}{r^2} \frac{\partial}{\partial r} (r^2 \etarho)
           +              \frac{\partial}{\partial r} (w_0 \rhozero) \right ] + \rho_0 \left(\frac{-2 w_0 g}{r} - 4 \pi G \etarho \right) \nonumber \\
&=& 
- \frac{g}{r^2} \frac{\partial (r^2 \etarho)}{\partial r} - \frac{4 (\ow + \dw) \rho_0 g}{r} 
- 4 \pi G \rhozero \etarho \label{eq:B7} \enskip .
\end{eqnarray}

\noindent We discretize this elliptic equation in the radial dimension as:
\begin{eqnarray}
&& \frac{1}{\Delta r} \left\{
\left[ \frac{\gammabar p_0}{r^2} \frac{\partial (r^2 \dw)}{\partial r} \right]_{i} -
\left[ \frac{\gammabar p_0}{r^2} \frac{\partial (r^2 \dw)}{\partial r} \right]_{i-1} \right\}
+ \left[ \frac{4 (r^2 \dw) \rho_0 g}{r^3} \right]_{i-\half} \nonumber\\
&=& 
- \frac{g_{i-\half}}{r_{i-\half}^2 \Delta r} 
\left[ \left( r^2 \etarho \right)_{i} - \left( r^2 \etarho  \right)_{i-1} \right] 
   - \left[ \frac{4 \ow \rho_0 g}{r} \right]_{i-\half}
   - \left[  4 \pi G \rhozero \etarho   \right]_{i-\half} \enskip , \nonumber
\end{eqnarray}
where we have chosen to solve for $(r^2 \dw)$ rather than $\dw.$
Then, using hydrostatic equilibrium, we expand this to 
\begin{eqnarray}
&& \frac{1}{\Delta r} \left\{
 \left( \frac{\gammabar p_0}{r^2}\right)_{i  } \frac{[ (r^2 \dw)_{i+\half} - (r^2 \dw)_{i-\half} ]}{\Delta r}
-\left( \frac{\gammabar p_0}{r^2}\right)_{i-1} \frac{[ (r^2 \dw)_{i-\half} - (r^2 \dw)_{i-\thalf}]}{\Delta r} \right\} \nonumber \\
&&  - \left\{ \frac{4}{r_{i-\half} ^3} \frac{{p_0}_i - {p_0}_{i-1}}{\dr} \right\} (r^2 \dw)_{i-\half}  \nonumber \\
&=&   \left\{ \frac{4}{r_{i-\half} ^3} \frac{{p_0}_i - {p_0}_{i-1}}{\dr} \right\} (r^2 \ow)_{i-\half}
 - \frac{g_{i-\half}}{r_{i-\half}^2 \Delta r} 
  \left[ \left( r^2 \etarho \right)_{i} - \left( r^2 \etarho  \right)_{i-1} \right] 
- \left[  4 \pi G \rhozero \etarho   \right]_{i-\half} \enskip.
\end{eqnarray}

If we write this in matrix form, so that:
\begin{equation}
A_i (r^2 \dw)_{i-\thalf} + B_i (r^2 \dw)_{i-\half} + C_i (r^2 \dw)_{i+\half} = F_i\enskip,
\end{equation}
then:
\begin{eqnarray}
A_i &=& \frac{1}{\Delta r^2} \left( \frac{\gammabar p_0}{r^2}\right)_{i-1}  \enskip, \nonumber  \\
B_i &=& -\frac{1}{\Delta r^2} \left[ \left( \frac{\gammabar p_0}{r^2}\right)_{i  }  
               +\left( \frac{\gammabar p_0}{r^2}\right)_{i-1} \right] 
              - \left\{ \frac{4}{r_{i-\half} ^3} \frac{{p_0}_i - {p_0}_{i-1}}{\dr} \right\} \nonumber \\
C_i &=& \frac{1}{\Delta r^2} \left( \frac{\gammabar p_0}{r^2}\right)_{i}  \enskip, \nonumber  \\
F_i &=&  \left\{ \frac{4}{r_{i-\half} ^3} \frac{{p_0}_i - {p_0}_{i-1}}{\dr} \right\} (r^2 \ow)_{i-\half}
 - \frac{g_{i-\half}}{r_{i-\half}^2 \Delta r} 
\left[ \left( r^2 \etarho \right)_{i} - \left( r^2 \etarho  \right)_{i-1} \right] 
- \left[  4 \pi G \rhozero \etarho   \right]_{i-\half} \enskip \nonumber .
\end{eqnarray}
Here,
\begin{equation}
g_{j-\half} = \frac{G}{r_{j-\half}^2} \sum_{k=1}^{j} \frac{4}{3} \pi  (r_{k-\half}^3 - r_{k-\thalf}^3) \; {\rho_0}_{k-1} \enskip.
\end{equation}

We define the lower boundary condition, $ \dw = 0$ at $r=0,$ which
corresponds to $i=1,$ by setting:
\begin{eqnarray}
A_1 = C_1 = F_1 &=& 0\enskip, \nonumber \\
B_1 &=& 1\enskip. \nonumber
\end{eqnarray}
We also specify $\partial (r^2 \dw) / \partial r = 0$ at the the upper boundary, which corresponds to $i=N,$
by setting:
\begin{eqnarray}
A_N &=& -1\enskip, \nonumber \\
B_N &=&  1\enskip, \nonumber \\
C_N = F_N &=& 0\enskip. \nonumber
\end{eqnarray}
\end{description}

@@

\item[spherical:] The base state density update now includes the area factors in the 
divergences:
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp}
 - \frac{1}{r_j^2} \frac{\dt}{\dr} 
 \left [ \left( r^2 \rho_0^{\outp,\nph} w_0^{\inp}\right)_{j+\myhalf} -  
          \left( r^2 \rho_0^{\outp,\nph} w_0^{\inp}\right)_{j-\myhalf} \right] \enskip. 
\end{equation}

\item {\bf Advect Base Pressure}
is the process by which we update the base state pressure through $\dt$ in time and
compute $\psi$.  The input arguments are different for plane-parallel and spherical.
\begin{description}
\item {\bf Advect Base Pressure Planar}$[p_0^\inp,w_0^\inp,\etarho^\inp] \rightarrow 
[p_0^\outp,\psi^\outp]$:

@@

>>>>

@@

\item[spherical:] The base state density update now includes the area factors in the 
divergences:
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp}
 - \frac{1}{r_j^2} \frac{\dt}{\dr} 
 \left [ \left( r^2 \rho_0^{\outp,\nph} w_0^{\inp}\right)_{j+\myhalf} -  
          \left( r^2 \rho_0^{\outp,\nph} w_0^{\inp}\right)_{j-\myhalf} \right] \enskip. 
\end{equation}
\end{description}
\item {\bf Advect Base Pressure}
is the process by which we update the base state pressure through $\dt$ in time and
compute $\psi$.  The input arguments are different for plane-parallel and spherical.
\begin{description}
\item {\bf Advect Base Pressure Planar}$[p_0^\inp,w_0^\inp,\etarho^\inp] \rightarrow 
[p_0^\outp,\psi^\outp]$:

@@

We begin with equation (23) in paper III written in spherical coordinates:
\[
\frac{1}{r^2}\frac{\partial}{\partial r} \left (r^2 \beta_0 w_0 \right ) =
\beta_0 \left ( \Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} \right )\enskip.
\]
We expand the spatial derivative and divide through by $\beta_0$:
\begin{equation}
\label{eq:sphconstraint}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0 \right ) +
w_0 \frac{1}{\beta_0} \frac{\partial \beta_0}{\partial r} =
 \Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t}  \enskip .
\end{equation}
Recalling from paper I that;
\[
\frac{1}{\gammabar p_0}  \frac{\partial p_0}{\partial r} = \frac{1}{\beta_0} \frac{\partial \beta_0}{\partial r}\enskip,
\]
and moving this term to the right hand side,
we can express equation (\ref{eq:sphconstraint}) as:
\begin{eqnarray}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 w_0 \right ) &=&
  \Sbar - \frac{1}{\gammabar p_0} \left( 
\frac{\partial p_0}{\partial t} + w_0 \frac{\partial p_0}{\partial r} \right)\enskip. \label{eq:w01}
\end{eqnarray}
We first solve a piece of this equation for $\ow = w_0 - \dw$:
\begin{eqnarray}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 \ow \right ) &=& \Sbar \enskip.
\end{eqnarray}
Then we can write
\begin{eqnarray}
\frac{1}{r^2} \frac{\partial}{\partial r} \left (r^2 \dw \right ) &=&
  - \frac{1}{\gammabar p_0} \left[
\frac{\partial p_0}{\partial t} + (\ow + \dw)
\frac{\partial p_0}{\partial r} \right]\enskip.\label{eq:w01a}
\end{eqnarray}

Multiplying equation (\ref{eq:w01a}) through by $\gammabar p_0 $,
taking another derivative with respect to $r$, and switching the order
of temporal and spatial derivatives, we get:
\begin{equation}
\label{eq:sphconstraint_2}
\frac{\partial}{\partial r} \left [ \frac{\gammabar p_0 }{r^2} \frac{\partial}{\partial r} (r^2 \dw) \right ]
= -\frac{\partial}{\partial t} \frac{\partial p_0}{\partial r}
  -\frac{\partial}{\partial r} \left [(\ow+\dw) \frac{\partial p_0}{\partial r} \right ]\enskip.
\end{equation}

To solve for $\dw$ we will need to substitute for the derivatives of $p_0.$
To do so we start with the equation of hydrostatic equilibrium in a spherical geometry:
\[
\frac{\partial p_0}{\partial r} = -\rho_0 g \, ; \quad
g = \frac{G m_\mathrm{encl}}{r^2}\enskip,
\]
where $m_\mathrm{encl}(r)$ is the mass enclosed at radius $r$ and $G$ is the
gravitational constant.  
Using this, we can then write equation (\ref{eq:sphconstraint_2}) as:
\begin{eqnarray}
\frac{\partial}{\partial r} \left[ \frac{\gammabar p_0}{r^2} \frac{\partial}{\partial r} (r^2 \dw) \right] &=&
 \frac{\partial}{\partial t} \left (\rho_0 g \right )
+\frac{\partial}{\partial r} \left (w_0 \rho_0 g \right) \nonumber \\
&=&
  g \left[ \frac{\partial \rho_0}{\partial t} + \frac{\partial}{\partial r} (w_0 \rho_0) \right]
+ \rho_0 \left( \frac{\partial g}{\partial t} + w_0 \frac{\partial g}{\partial r} \right) \enskip.\nonumber\\
&&
\label{eq:sphconstraint_3}
\end{eqnarray}
The mass enclosed inside any radius, $r$, is $m_\mathrm{encl}(r) = 4 \pi
\int_0^r \rhozero(s) s^2 ds$, or alternately, $\partial m_\mathrm{encl}/\partial r = 4\pi r^2 \rho_0$.  
The Lagrangian derivative of the enclosed mass is then:
\begin{eqnarray}
\frac{D_0 m_\mathrm{encl}}{D t} &=& \frac{\partial m_\mathrm{encl}}{\partial t} + w_0 \frac{\partial m_\mathrm{encl}}{\partial r} \nonumber \\
 &=& 4\pi \left( \frac{\partial}{\partial t} \int_0^r \rhozero(s) s^2 ds + w_0 r^2 \rho_0 \right) \nonumber \\
&=& 4\pi \left( \int_0^r \frac{\partial \rho_0}{\partial t} s^2 ds + w_0 r^2 \rho_0 \right) \nonumber \\
&=& 4\pi \left\{ -\int_0^r \left [ \frac{1}{s^2}\frac{\partial(s^2 \rho_0 w_0)}{\partial s} + \frac{1}{s^2}\frac{\partial (s^2 \etarho)}{\partial s} \right ]s^2 ds + w_0 r^2 \rho_0 \right\} \nonumber \\
&=&  \left . 4\pi \left(-s^2 \rho_0 w_0 \right |_0^r - \left . s^2 \etarho \right |_0^r + w_0 r^2 \rho_0 \right) \nonumber \\
&=& -4\pi r^2 \etarho \label{eq:dmdt}
\end{eqnarray}
where we used the spherical form of equation (29) in paper III, 
\begin{equation}
\label{eq:sph_continuity}
\frac{\partial \rhozero}{\partial t} + \frac{1}{r^2} \frac{\partial (r^2 \rho_0 w_0)}{\partial r} 
+ \frac{1}{r^2} \frac{\partial (r^2 \etarho )}{\partial r}  = 0 \enskip ,
\end{equation}
to eliminate $\partial \rho_0/\partial t$.  We note that in the
absence of any mixing, $\etarho=0$, and  $D_0 m_\mathrm{encl}/Dt = 0.$
Equation (\ref{eq:dmdt})
allows us to write the Lagrangian change in the gravitational
acceleration as:
\begin{eqnarray}
\frac{D_0 g}{D t} = \frac{\partial g}{\partial t} + w_0 \frac{\partial g}{\partial r} &=& \frac{D_0}{Dt}\left(\frac{G m_\mathrm{encl}}{r^2}\right) \nonumber \\
&=& G m_\mathrm{encl}\frac{D_0}{D t}\left(\frac{1}{r^2}\right) + \frac{G}{r^2}\frac{D_0 m_\mathrm{encl}}{Dt} \nonumber \\
&=& -\frac{2 w_0 G m_\mathrm{encl}}{r^3} - 4 \pi G \etarho \nonumber \\
&=& -\frac{2 w_0 g}{r} - 4 \pi G \etarho \enskip .
\end{eqnarray}

Putting it all together, equation (\ref{eq:sphconstraint_3}) becomes:
\begin{equation}
 \frac{\partial}{\partial r} \left[ \frac{\gammabar p_0}{r^2} \frac{\partial}{\partial r} (r^2 \dw) \right] 
= 
  g \left [ \frac{\partial \rho_0}{\partial t} + \frac{\partial}{\partial r} (w_0 \rho_0) \right ]
+ \rho_0 \left(\frac{-2 w_0 g}{r} - 4 \pi G \etarho \right) \label{eq:B5} \enskip.
\end{equation}
Finally, we can use equation (\ref{eq:sph_continuity})
to write equation (\ref{eq:B5}) as:
\begin{eqnarray}
\frac{\partial}{\partial r} \left[ \frac{\gammabar p_0}{r^2} \frac{\partial}{\partial r} (r^2 \dw) \right] &=&
 g \left [ -\frac{1}{r^2} \frac{\partial}{\partial r} (r^2 w_0 \rhozero)
           -\frac{1}{r^2} \frac{\partial}{\partial r} (r^2 \etarho)
           + \frac{\partial}{\partial r} (w_0 \rhozero) \right ] \nonumber \\
&& + \rho_0 \left(\frac{-2 w_0 g}{r} - 4 \pi G \etarho \right) \nonumber \\
&=& - \frac{g}{r^2} \frac{\partial (r^2 \etarho)}{\partial r} 
- \frac{4 (\ow + \dw) \rho_0 g}{r} - 4 \pi G \rhozero \etarho \label{eq:B7} \enskip .
\end{eqnarray}

\noindent We discretize this elliptic equation in the radial dimension as:
\begin{eqnarray}
&& \frac{1}{\Delta r} \left\{
\left[ \frac{\gammabar p_0}{r^2} \frac{\partial (r^2 \dw)}{\partial r} \right]_{j} -
\left[ \frac{\gammabar p_0}{r^2} \frac{\partial (r^2 \dw)}{\partial r} \right]_{j-1} \right\}
+ \left[ \frac{4 (r^2 \dw) \rho_0 g}{r^3} \right]_{j-\myhalf} \nonumber\\
&=& 
- \frac{g_{j-\myhalf}}{r_{j-\myhalf}^2 \Delta r} 
\left[ \left( r^2 \etarho \right)_{j} - \left( r^2 \etarho  \right)_{j-1} \right] 
   - \left( \frac{4 \ow \rho_0 g}{r} \right)_{j-\myhalf}
   - \left(  4 \pi G \rhozero \etarho   \right)_{j-\myhalf} \enskip , \nonumber
\end{eqnarray}
where we have chosen to solve for $(r^2 \dw)$ rather than $\dw.$
Then, using hydrostatic equilibrium, we expand this to 
\begin{eqnarray}
&& \frac{1}{\Delta r} \left\{
 \left( \frac{\gammabar p_0}{r^2}\right)_{j  } \frac{\left[ (r^2 \dw)_{j+\myhalf} - (r^2 \dw)_{j-\myhalf} \right]}{\Delta r}
-\left( \frac{\gammabar p_0}{r^2}\right)_{j-1} \frac{\left[ (r^2 \dw)_{j-\myhalf} - (r^2 \dw)_{j-\thalf}\right]}{\Delta r} \right\} \nonumber \\
&&  - \left( \frac{4}{r_{j-\myhalf} ^3} \frac{p_{0,i} - p_{0,i-1}}{\dr} \right) (r^2 \dw)_{j-\myhalf}  \nonumber \\
&=&   \left( \frac{4}{r_{j-\myhalf} ^3} \frac{p_{0,i} - p_{0,i-1}}{\dr} \right) (r^2 \ow)_{j-\myhalf}
 - \frac{g_{j-\myhalf}}{r_{j-\myhalf}^2 \Delta r} 
  \left[ \left( r^2 \etarho \right)_{j} - \left( r^2 \etarho  \right)_{j-1} \right] 
- \left(  4 \pi G \rhozero \etarho   \right)_{j-\myhalf} \enskip. \nonumber \\
\end{eqnarray}

If we write this in matrix form, so that:
\begin{equation}
A_j (r^2 \dw)_{j-\thalf} + B_j (r^2 \dw)_{j-\myhalf} + C_j (r^2 \dw)_{j+\myhalf} = F_j\enskip,
\end{equation}
then:
\begin{eqnarray}
A_j &=& \frac{1}{\Delta r^2} \left( \frac{\gammabar p_0}{r^2}\right)_{j-1}  \enskip, \nonumber  \\
B_j &=& -\frac{1}{\Delta r^2} \left[ \left( \frac{\gammabar p_0}{r^2}\right)_{j  }  
               +\left( \frac{\gammabar p_0}{r^2}\right)_{j-1} \right] 
              - \left( \frac{4}{r_{j-\myhalf} ^3} \frac{p_{0,i} - p_{0,i-1}}{\dr} \right) \nonumber \\
C_j &=& \frac{1}{\Delta r^2} \left( \frac{\gammabar p_0}{r^2}\right)_{j}  \enskip, \nonumber  \\
F_j &=&  \left( \frac{4}{r_{j-\myhalf} ^3} \frac{p_{0,i} - p_{0,i-1}}{\dr} \right) (r^2 \ow)_{j-\myhalf}
 - \frac{g_{j-\myhalf}}{r_{j-\myhalf}^2 \Delta r} 
\left[ \left( r^2 \etarho \right)_{j} - \left( r^2 \etarho  \right)_{j-1} \right] 
- \left(  4 \pi G \rhozero \etarho   \right)_{j-\myhalf} \enskip \nonumber .
\end{eqnarray}
Here,
\begin{equation}
g_{j-\myhalf} = \frac{G}{r_{j-\myhalf}^2} \sum_{k=1}^{j} \frac{4}{3} \pi  (r_{k-\myhalf}^3 - r_{k-\thalf}^3) \; {\rho_0}_{k-1} \enskip.
\end{equation}

We define the lower boundary condition, $ \dw = 0$ at $r=0,$ which
corresponds to $j=1,$ by setting:
\begin{eqnarray}
A_1 = C_1 = F_1 &=& 0\enskip, \nonumber \\
B_1 &=& 1\enskip. \nonumber
\end{eqnarray}
We also specify $\partial (r^2 \dw) / \partial r = 0$ at the the upper boundary, which corresponds to $j=N,$
by setting:
\begin{eqnarray}
A_N &=& -1\enskip, \nonumber \\
B_N &=&  1\enskip, \nonumber \\
C_N = F_N &=& 0\enskip. \nonumber
\end{eqnarray}
\end{description}
